\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-06-18 paper/paper 2/dc-2015-abstract.tex
Final Abstract and Title

\title{\vspace{-1em}Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box}

@@

%When using the developed vocabulary to intermediately represent constraints,
%depending on the individual type of constraint one or multiple particular constraining elements are applied.
%We base these constraining elements on formal logic.
%As constraints of 2/3 of all constraint types are expressible by logical constructs from description logics,
%we may use logical constructs as constraining elements.
%In order to be able to support all constraint types, however,
%we determined for each constraint type more intuitive constraining elements in natural language like \emph{conditional properties}, \emph{allowed values}, and \emph{language tag minimum cardinality}.
%A title is required for books.
%This constraint of the constraint type \emph{required properties (R-68)} can be either expressed by the existential quantifier $\exists$ from description logics or more intuitively using the constraining element \emph{required properties}.

%As SPARQL is generally seen as the method of choice to validate data according to certain constraints and
%as RDF data can be validated on constraints of any constraint type by means of SPARQL,
%we use SPIN, a SPARQL-based way to validate RDF data, as implementation language 
%to actually execute the validation of RDF data.
%Thereby, constraints may either be 
%(1) expressed by domain specific constraint languages like OWL 2 and DSP or
%(2) represented by the proposed vocabulary.

%The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
%In this paper, we provide a basic terminology and classification system for RDF constraints.\tb{The contributions of this paper are the following. (1)...}
%We developed a vocabulary to describe constraints of any RDF constraint type generically. 
%%(whether expressible in description logics or not).
%We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful.
%We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages by providing mappings to generically expressed constraints.

%The main contributions of this paper are:
%(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
%(2) As current high-level constraint languages do not support all constraint types, 
%we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics.
%(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
%to intermediately represent constraints 
%%as an intermediate generic representation 
%which enables transformations between semantically equivalent constraints.
%(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type.

\hspace{-1.4em}
\textbf{Keywords:}
RDF validation; RDF constraints; RDF constraint types, RDF validation requirements; Linked Data; Semantic Web

\section{Introduction}
%The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
%OWL 2 is based on the {\em non-unique name assumption} (nUNA) whereas RDF validation requires that different names represent different objects ({\em unique name assumption} (UNA)). 
%Reasoning in OWL 2 is based on the semantics of {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose: to represent knowledge on the World Wide Web. 
%On the other hand, many RDF validation scenarios require the {\em closed-world assumption} (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
%This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation.  
%For this reason, we cannot use OWL 2 ontologies for RDF validation as we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.

Recently, RDF validation as a research field gained speed due to common needs of data practitioners. A typical example is the library domain that co-developed and adopted Linked Data principles very early. For libraries, the common description of resources are key business and they have a long tradition in developing and using interoperable data formats. While they embrace the openness of Linked Data and the data modeling principles provided by RDF, the data is still mostly represented in XML and this is unlikely to change any time soon. 
Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like \emph{DTD}, \emph{XML Schema}, \emph{RELAX NG}, or \emph{Schematron}.
A typical example is the definition of a library record describing a book. There are clear rules which information has to be available to describe a book properly, but also how information like an ISBN number is properly represented. Libraries seek to make their own data reusable for general purposes, but also to enrich and interlink their own data. Checking if third-party data meets own requirements or validating existing data according to new needs for a Linked Data application are among common use cases for RDF validation.

In 2013, the \emph{W3C} organized the \emph{RDF Validation Workshop}\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}
where experts from industry, government, and academia discussed first RDF validation use cases. 
%for RDF data validation and constraint formulation.
In 2014, two working groups on RDF validation have been established: 
the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}. 
We collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at \url{http://purl.org/net/rdf-validation}}
with the intention to collaboratively collect case studies, use cases, requirements, and solutions in a comprehensive and structured way \cite{BoschEckert2014}. 
Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
we published by today 81 requirements to validate RDF data and to formulate constraints; 
%each of them corresponding to a constraint type which in most cases can be expressed by multiple constraint languages. 
each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data. 
%and which in most cases can be expressed by multiple constraint languages.
%Requirements/constraint types are uniquely identified by alphanumeric technical identifiers.
%\emph{Minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}, e.g., is a constraint type which corresponds to the requirement {\small\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}.
We recently published a technical report (serving as first appendix of this paper) in which we explain each constraint type in detail and give examples for each represented by different constraint languages \cite{BoschNolleAcarEckert2015}.
More than 10 constraint languages with different syntax and semantics exist or are currently developed. 
We focus on the five most promising ones on being the standard like
\emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, and \emph{Description Set Profiles (DSP)}. 
The \emph{Web Ontology Language} \emph{(OWL)} in its current version \emph{OWL 2} can also be used as a constraint language.
With its direct support of validation via \emph{SPARQL}, the \emph{SPARQL Inferencing Notation (SPIN)} is very popular and certainly plays an important role for the future development in this field. 
%\emph{SPIN} is particularly interesting as a means to validate arbitrary constraint languages by mapping them to \emph{SPARQL} \cite{BoschEckert2014-2}.

\subsection{Motivation and Overview}

We evaluated which constraint types the five most common constraint languages enable to express \cite{BoschNolleAcarEckert2015}.
%The evaluation is explained in detail in the appendix of this paper \cite{BoschNolleAcarEckert2015}.
Table \ref{tab:constraint-type-specific-expressivity} shows in percentage values (and absolute numbers in brackets) how many constraint types each language supports.

\begin{table}[H]
	\centering
	  %\caption{Constraint Type Specific Expressivity}
		\caption{Constraint Type Specific Expressivity of Constraint Languages}
	  \scriptsize
		\begin{tabular}{c|c|c|c|c}
      %\textbf{Expressivity Class} & $Expr(\overline{\mathcal{CT}_R})$ (42) & $Expr(\mathcal{CT}_R)$ (32) \\		
			\emph{DSP} & \emph{ReSh} & \emph{ShEx} & \emph{OWL 2} & \emph{SPIN} \\	
      \hline
			17.3 (14) & 25.9 (21) & 29.6 (24) & 67.9 (55) & \textbf{100.0} \textbf{(81)} 
		\end{tabular}
	\label{tab:constraint-type-specific-expressivity}
\end{table}

The fact that \emph{SPIN} supports all and \emph{OWL 2} covers 2/3 of all constraint types
emphasizes the significant role \emph{SPIN} and \emph{OWL 2} play for the future development of constraint languages.
\emph{SPARQL} and therefore \emph{SPIN}, the \emph{SPARQL}-based way to formulate and check constraints, is generally seen as the method of choice to validate data according to certain constraints \cite{Fuerber2010}, 
although, it is not ideal for their formulation. 
In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
Declarative languages may be placed on top of \emph{SPARQL} and \emph{SPIN} when using them as implementation languages.

There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
%which can be used to express constraints and to validate RDF data, 
%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
%\section{Ideas}
%constraint design patterns:
% - ontology design pattern.org
% - DSP uses other design pattern
% - constraint elements are the same / 
% - constraint / constraint elements / constraint design patterns / constraint language
%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
%min car more powerful than req. propery
Thus, the idea behind this paper is to satisfy all RDF validation requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
We lately published a technical report (serving as second appendix of this paper) in which we describe the vocabulary in detail \cite{BoschEckert2015-2} (Section \ref{sec:vocabulary}).
The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75} can be instantiated to ensure
that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
%As every \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
As the book \emph{The-Lord-Of-The-Rings} is a \emph{publication}, 
%{\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
it must have at least one \emph{author} relationship to a \emph{person}.
The constraint is violated either (1) if
the book does not have any \emph{author} relationship, 
or (2) if it has an \emph{author} which is not a \emph{person},
%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)},} {\small\ms{rdf:type(Tolkien, Hobbit)),}} 
or (3) if it has an \emph{author} whose class is unknown.
%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
%In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}.
%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}
This constraint can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}} or specifically (\emph{specific constraint}) by multiple domain-specific constraint languages:

\begin{ex}[commandchars=\\\{\}]
\textit{OWL 2:} Publication a owl:Restriction ;
          owl:minQualifiedCardinality 1 ;
          owl:onProperty author ;
          owl:onClass Person .

\textit{ShEx:} Publication \{ author @Person\{1, \} \}

\textit{ReSh:} Publication a rs:ResourceShape ; rs:property [
          rs:propertyDefinition author ;
          rs:valueShape Person ;
          rs:occurs rs:One-or-many ; ] .

\textit{DSP:} [ dsp:resourceClass Publication ; dsp:statementTemplate [ 
          dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
          dsp:property author ; 
          dsp:nonLiteralConstraint [ dsp:valueClass Person ] ] ] .

\textit{SPIN:} CONSTRUCT \{ [ a spin:ConstraintViolation ... . ] \} WHERE \{ 
          ?this ?p ?o ; a ?C .
          BIND ( \textit{qualifiedCardinality}( ?this, ?p, ?C ) AS ?c ) .
          BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality ) .
          FILTER ( ?cardinality < ?minimumCardinality ) . \}

\textit{SPIN function qualifiedCardinality:}										
SELECT ( COUNT ( ?arg1 ) AS ?c ) WHERE \{ ?arg1 ?arg2 ?o . ?o a ?arg3 . \}
\end{ex}

The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
For this reason, we mapped constraint types to \emph{DL} 
in order to determine which \emph{DL} constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.

The main contributions of this paper are:
(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation (Section \ref{sec:vocabulary}).
(2) As current high-level constraint languages do not support all constraint types, 
we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics (Section \ref{sec:vocabulary}).
(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
to intermediately represent constraints 
%as an intermediate generic representation 
which enables transformations between semantically equivalent constraints (Section \ref{sec:transformations}).
(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type (Section \ref{sec:validation}).

\subsection{How to Improve the Interoperability of RDF Constraints}
\label{sec:transformations}

RDF data providers have to ensure high data quality and therefore 
that their data conforms to constraints which may be part of contracts between data providers and consumers.
As there is no standard way to formulate constraints, 
semantically equivalent \emph{specific constraints}, so the \emph{minimum qualified cardinality restriction}, may be represented by a variety of languages - each of them having different syntax and semantics.
This causes confusion and weakens the common understanding between several parties about the meaning of particular constraints.
We propose transformations between semantically equivalent \emph{specific constraints}
(1) to avoid the necessity to understand several languages,
(2) to resolve misunderstandings about the meaning of particular constraints within the communication of RDF data producers and consumers, and
(3) to enhance the interoperability of constraint languages.

We suggest to transform a \emph{specific constraint} (\emph{$sc_{\alpha}$}) of any constraint type expressed by language \emph{$\alpha$} into a semantically equivalent \emph{specific constraint} (\emph{$sc_{\beta}$}) of the same constraint type represented by any other language \emph{$\beta$}
by using the developed vocabulary to intermediately represent constraints in a generic way. 
%to enable these transformations.
By defining mappings between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically: 
{\small\ms{$ gc = m_1(sc_{\alpha}) = m_2(sc_{\beta}) $}}.
Thereby, we do not need to define mappings between each pair of semantically equivalent \emph{specific constraints}.
Let's assume we are able to express constraints of the \emph{minimum qualified cardinality restrictions} constraint type by 10 languages.
Without an intermediate generic representation of constraints, we would have to define for each constraint type one mapping between each pair of \emph{specific constraints} expressed by \emph{n} languages
- that are \emph{\( {n \choose 2} \)} mappings (\emph{\( {10 \choose 2} \)} = 45 mappings).
With an intermediate generic representation of constraints, on the other side, we only need to define for each constraint type \emph{n} mappings 
%(1 mapping for each \emph{specific constraint}) 
from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (10 mappings).
%Let's assume we are able to express a particular constraint type by 5/6/7/8/9/10 constraint languages.
%Without the intermediate \emph{generic constraint}, we would have to define for each constraint type \emph{1} mapping for each pair of \emph{specific constraints} (expressed by different constraint languages)
%that are \emph{\( {n \choose 2} \)} mappings (10/15/21/28/36/45 mappings).
%With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (1 mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (5/6/7/8/9/10 mappings).
For the \emph{minimum qualified cardinality restriction}, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ShEx})$}, \emph{$m_3(sc_{ReSh})$}, \emph{$m_4(sc_{DSP})$},...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ShEx}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{DSP}$},...) to the corresponding \emph{generic constraint} (\emph{gc}).

\subsection{How to Provide the Validation of RDF Constraints Out-Of-The-Box}
\label{sec:validation}

We use \emph{SPIN} as basis to develop a validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footnote{\emph{SPIN} mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}\label{spin-mappings}} \cite{BoschEckert2014-2}.
The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations \cite{BoschEckert2014-2}.
The next step, however, was to extend the \emph{RDF Validator} to validate RDF data conforming to constraints of any constraint type
by representing constraints generically using the proposed vocabulary.

When language designers extend constraint languages 
to be able to formulate constraints of not yet supported constraint types,
our proposal prevents the necessity to actually implement the validation of data
according to constraints of these constraint types for each of those languages.  
For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
%validation implementations out-of-the-box for any constraint type whose \emph{specific constraints} may be expressed by any language  
by providing a \emph{SPIN} mapping
%generic validation implementations once 
for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}  
whose constraints are represented generically \cite{BoschEckert2015-2}.
%(2) by transforming \emph{specific constraints} into the appropriate \emph{generic constraint}.  
All what language designers need to do is to specify for each constraint type they want to cover one mapping from the \emph{specific constraint} expressed by the language to the corresponding \emph{generic constraint}.
19 of the overall 81 constraint types are expressible by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
This means that for these 19 constraint types there must be 76 implementations (four for each constraint type) to actually validate RDF data according to 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}). 
%which lead for each constraint type to identical validation results independently from the language used to formulate the \emph{specific constraints}.
Our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
leads to exactly the same validation results, 
i.e., that validation is performed independently from the used language.
This is not the case, however, for existing languages due to differences in semantics and since they are implemented independently form each other.

%When domain experts use graphical user interfaces to define constraints in a user-friendly way (without the necessity to express constraints on their own), 
%constraints can be mapped to either a specific or a generic constraint, as for both the validation is provided in the background.    
%So, the user does not have to know how to express specific constraints using any constraint language.

%Existing constraint languages can be extended and new constraint languages can be developed, if existing constraint languages are not sufficient to represent needed constraint types.

%If (1) a new constraint type is expressed generically, (2) the \emph{generic constraint type} is mapped to \emph{specific constraint types} (expressed by constraint languages), and (3) the validation is implemented for this particular \emph{generic constraint type},
%the validation of \emph{specific constraint types} is provided out of the box.
%As a consequence, constraint language designers do not have to implement the validation of their constraint languages and each semantically equivalent \emph{specific constraint type} is validated the same way (i.e. leading to identical validation results).

%This paper aims to address two main \textbf{audiences}:
%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and  
%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.

%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)

%The remainder of the paper is as follows.

%\begin{itemize}
	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
	%\item We define a basic terminology and classification system for RDF constraints
	%\item We developed an ontology describing any RDF constraint generically (whether expressible in DL or not)%which can also be expressed by any constraint language
	%\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
	%\item We show how to transform specific constraints (expressed by any constraint language \ms{$\alpha$}) into generic constraints and into specific constraints (expressed by any other constraint language \ms{$\beta$})
  %\item We explain that any specific constraint can be validated automatically (if the validation is implemented only once for the corresponding generic constraint)
%\end{itemize}

%The \textbf{benefits} of our framework are:
%\begin{itemize}
	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
%\end{itemize}

%\section{Running Example}
%
%Table \ref{tab:cardinality-restriction-mapped-to-vocabulary} shows the mapping between the \emph{cardinality restriction} represented in DL 
%and the \emph{cardinality restriction} expressed by our developed vocabulary to describe any RDF constraint generically (see section~\ref{sec:ontology}):
%
%\begin{table}
  %\scriptsize
  %\sffamily
  %\vspace{0cm}
	%\centering
		%\begin{tabular}{l|l|l|l|l|l|l}
      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      %\hline
      %property & Publication & author & - & Person & $\geq$ & 1 \\
		%\end{tabular}
	%\caption{Cardinality Restriction Expressed Generically}
	%\label{tab:cardinality-restriction-mapped-to-vocabulary}
%\end{table}

%According to this vocabulary, each constraint is either a constraint on classes or a constraint on properties.
%The generically expressed cardinality restriction is represented in RDF as follows:
%
%\begin{ex}
%[   a PropertyConstraint ;
    %contextClass Publication ;
    %leftProperties ( author ) ;
    %classes ( Person ) ;
    %constrainingElement ">=" ;
    %constrainingValue 1 ] .
%\end{ex}

%Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
%validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL. 
%The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
%The generically expressed \emph{cardinality restriction} above is validated within the validation environment (see section \ref{sec:validation}) by means of a SPARQL CONSTRUCT query.

%\begin{ex}
%[   a PropertyConstraint ;
    %contextClass ?cc ;
    %leftProperties ( ?p1 ) ;
    %classes ( ?c1 ) ;
    %constrainingElement ">=" ;
    %constrainingValue ?cv ] .
%?subject rdf:type ?cc .
%BIND ( qualifiedCardinality( ?subject, ?p1, ?c1 ) AS ?c ) .
%FILTER ( ?c < ?cv ) .		  
%\end{ex}

\section{A Vocabulary to Describe RDF Constraints Generically} 
\label{sec:vocabulary}

Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on validation.

\subsection{Semantics for RDF Validation}

RDF validation and \emph{OWL 2} assume different semantics. 
This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.
We compare semantics of RDF validation and \emph{OWL 2} as \emph{OWL 2} is considered as a constraint language 
when validation semantics is applied.
%
\emph{OWL 2} is based on the {\em open-world assumption} (\emph{OWA}), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the \emph{WWW}. 
As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book}, %{\small\ms{(Book(Hamlet)),}}
{\em Hamlet} must have at least one \emph{title}.
In an \emph{OWA} setting, this constraint does not cause a violation, even if there is no explicitly defined \emph{title}, since there must be a \emph{title} for this \emph{book} which we may not know. 
%($\mathcal{K}$ is consistent).
As RDF validation has its origin in the XML world
many RDF validation scenarios require the {\em closed-world assumption} (\emph{CWA}), i.e., a statement is inferred to be false if it cannot be proved to be true.
Thus, classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals. 
The \emph{CWA} yields to a violation since there is no explicitly defined \emph{title} for the \emph{book} {\em Hamlet}. 
%
Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
If we define the property \emph{title} to be functional {\small\ms{(funct (title)),}} a \emph{book} can have at most one distinct \emph{title}.
\emph{UNA} causes a clash
if the \emph{book} {\em Huckleberry-Finn} has more than one \emph{title}.
For \emph{nUNA}, however, reasoning concludes that the \emph{title} {\em The-Adventures-of-Huckleberry-Finn} must be the same as the \emph{title} {\em Die-Abenteuer-des-Huckleberry-Finn} 
which resolves the violation. 
%Although, \emph{OWL 2} does not assume \emph{UNA}, \emph{OWL 2} has the constructs \emph{owl:sameAs} and \emph{owl:differentFrom} to state that two names are the same or different.
If validation would assume \emph{OWA} and \emph{nUNA}, validation won’t be that restrictive and therefore we won’t get the intended validation results.
%
%\emph{OWL 2} reasoning is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
%%which fits its primary design purpose to represent knowledge on the World Wide Web. 
%%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
%%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
%%\tb{the following example does not show the redundancy problem!}
%%\tb{2. benefit: reasoning solves redundancy problem}
%As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
%{\em Hamlet} must have at least one \emph{title}.
%In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know. 
%On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
%When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
%A constraint that says that a book must have at least one title in \emph{OWA}, 
%does not mean that the title has to be unique. 
%In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
%it can be the case that a book has a single title, however, 
%this title is not unique. 
%In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
%And since in every model there is only one, \emph{DL} sentences are satisfied. 
%But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
%%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
%This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
%\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this. / Thomas: I think your issue is tackled now? No.}
%
%comments from Erman:
%
%\begin{itemize}
%\item If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other. We have to provide formal generic semantics for it; formally prove those statements.}
%
%\item This is simple. You write that:
%In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general.
%The question is how to adopt CWA for OWL2, because it wont behave CWA way, just because we want it. So I say, in order to show that it behaves exactly we want it to, we should show that for the cases that we express a constraint (that we speak) in a classical constraint language, say, Scheme (therefore CWA) and  also OWL,  whenever the constraint in Scheme is violated, it's OWL correspondence is also violated. That shows that they behave in the same way, as they should. 
%
%\item So if you read again my comment again, without knowing which semantics those constraint languages have, one actually does is to show, given an RDF-data it is violated in one language iff it is violated in other. And this actually corresponds to the very idea of transformation and generic semantics. 
%
%\item Now, what is a generic semantics? 
%It is, the semantics we had in our mind, when typing this long document, that we tried to underpin by the DL language. However, regarding CWA and OWA, it is possible that we made some mistakes. In order to ensure that, say, if its DL, one needs to show that, a constraint/query written a particular language should have the same answer with its correspondent DL query.
%\end{itemize}
%
Differences in semantics may lead to differences in validation results when applied to particular constraint types.
This is important 
as for 56.8\% of the constraint types validation results differ if the \emph{CWA} or the \emph{OWA} 
and as for 66.6\% of the constraint types validation results are different in case the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.

Constraints are identical w.r.t. RDF semantics, 
if they detect the same set of violations regardless of RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations.
As we use multiple languages to express constraints of constraint types, 
%in the first appendix of this paper,
we thereby document identical semantics of these languages with regard to given constraint types \cite{BoschNolleAcarEckert2015}.
This is also important to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
behave in the same way w.r.t. validation results which semantically underpins bidirectional mappings.

%We defined the \textbf{formal generic semantics of the vocabulary} to describe constraints of any constraint type in a generic way (see paper appendix):
%(1) We mapped constraint types to \emph{DL} to logically underpin them and 
%(2) we described the constraint types' intended behavior in terms of validation results depending on \emph{CWA} and \emph{UNA}.
%To be able to define mappings between \emph{specific constraints} (expressed by different languages) and \emph{generic constraints},
%we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding \emph{DL} query.
%To be able to specify transformations between \emph{specific constraints} (expressed by different languages),
%identical semantics of the languages with regard to the particular constraint type has to be ensured.
%%Constraint languages assume identical semantics, 
%%if for each constraint the following condition holds:
%If a constraint is represented by \emph{ShEx} and \emph{OWL 2}, 
%the validation results must be exactly the same, i.e.,
%whenever the \emph{specific constraint} \emph{$sc_{ShEx}$} is violated, its \emph{$sc_{OWL 2}$} correspondence is also violated which shows that they behave in the same way.
%We expressed constraint types by different languages
%to document identical semantics for these languages with regard to appropriate constraint types.

%\textcolor{red}{feedback from Erman:}

%\textcolor{red}{
%-About the paragraph; it says we defined a formal generic semantics. Did we? (if you think so please defend) but i think its not true. A formal semantics, is where you talk about an interpretation e.g., like in DL, there the semantics/interpretation is a mathematical object (therefore formally defined). What i believe is that paper propose  rather a schema for transforming constraint languages to one another (in particular to assess them in the first paper), that a person who doesn't know one language can have operation power etc.. .
%}
%
%\textcolor{red}{
%-so I think we should get rid of this paragraph either totally or partially and you talk about the formulation instead briefly one-two sentence. I know that you wrote this paragraph to make my points and thanks a lot for that, but they were general remarks, so we cannot point out something that we do not do at that point, if its not at the "future work" or smth. Also this underpininng and  so on, these things were in the other paper (arxiv).  If it has a point, then better referencing it.
%}

%\textcolor{red}{
%-please be careful with the narration:
%To be able to define mappings between specific constraints (expressed by different languages) and generic constraints, we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding DL query. 
%When you read it and next sentence, it does not flow.  I know that it is not easy to write it nicely. But it also has technical problems, like
%}
%
%\textcolor{red}{
%A constraint  that is expected to give the same answer with a query. Those things are not of the same type. When I have written this query/constraint analogy, it was rather to provide an intuition. If we gonna talk about constraints; a constraint written in different languages always have the same restriction on any possible rdf-data. This means, if any two constraints are semantically the same (w.r.t. RDF data semantics), they should detect the same set of violations regardless of RDF data (which means whenever you apply them to any rdf data they point out the same violations or they have the same effect). Using a query language for validation, is a related but another thing. You actually know what it is better than I do.
%}

%Erman:
%Section 3.1, explains a possible application only in an example specific to UNA and nUNA case, and I also have the 
%feeling that it is so spread out to the whole work (paper1  especially), and in the core of technical parts. That is, whenever we mean CWA vs. OWA, we turn our head to UNA vs. nUNA.
%
%The thing I wanted to point out is that, the difference in CWA and OWA and its consequence/incompatibility is more general (as you also may probably noticed)  than the use of "UNA vs. nUNA".   The example I gave  is independent from the assumption of UNA  or nUNA. 
%
%You don't need to change something asap, but I think we can improve the exposition of any paper, by giving a classical constraint, how it is done classical in CWA, and how it is done in OWA, and then introducing the extra benefit, redundancy for instance.
%
%A constraint that says book should have a single author in OWA, does not mean that it has a unique author. In every model  (an interpretation that makes a set of DL knowledge base true), it can be the case that a book has a single author, however, bringing all those together, this author is not unique. In some models it is Ali, in others its Veli. And since in every model there is only one, DL sentences are satisfied. But this does not correspond to the intended constraint which is usual in CWA way.

\subsection{Basic Terminology and Classification System for RDF Constraints}
%\subsection{Basic Terminology for the Formulation of RDF Constraints}

>>>>

\title{\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.}

@@

%\listoftodos
\end{document}
